### 2015-08-10 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/AxiSEM_modif_for_coupling_with_specfem/MANUAL/manual_axisem1.2.tex
Clean NEW Axisem DIR ==> 2

(1) Tarje Nissen-Meyer, M. van Driel, S. C. Stähler, K. Hosseini, S. Hempel, L. Auer, 
A. Colombi, and A. Fournier (2014), \textit{AxiSEM: broadband 3-D seismic wavefields
in axisymmetric media},  Solid Earth, 5, 425-445. \\
doi:10.5194/se-5-425-2014\\

@@

(6) Martin van Driel and Tarje Nissen-Meyer (2014),
\textit{Seismic Wave Propagation in Fully Anisotropic Axisymmetric Media},
Geophysical Journal International 199 (2), 880–893.\\
doi:10.1093/gji/ggu269.\\

(7) Martin van Driel and Tarje Nissen-Meyer (2014),
\textit{Optimized Viscoelastic Wave Propagation for Weakly Dissipative Media},
Geophysical Journal International 199 (2) 1078–1093.\\
doi:10.1093/gji/ggu314.\\

@@

(8) Martin van Driel, Lion Krischer, Simon Stähler, Kasra Hosseini, and Tarje Nissen-Meyer (2015),
\textit{Instaseis: Instant Global Broadband Seismograms Based on a Waveform Database},
To be submitted to Solid Earth\\

>>>>

(1) Tarje Nissen-Meyer, M. van Driel, S. C. Stahler, K. Hosseini, S. Hempel, L. Auer,
A. Colombi, and A. Fournier (2014), \textit{AxiSEM: broadband 3-D seismic wavefields
in axisymmetric media},  Solid Earth, 5, 425-445. \\
doi:10.5194/se-5-425-2014\\

@@

(6) Martin van Driel and Tarje Nissen-Meyer (2014),
\textit{Seismic Wave Propagation in Fully Anisotropic Axisymmetric Media},
Geophysical Journal International 199 (2), 880-893.\\
doi:10.1093/gji/ggu269.\\

(7) Martin van Driel and Tarje Nissen-Meyer (2014),
\textit{Optimized Viscoelastic Wave Propagation for Weakly Dissipative Media},
Geophysical Journal International 199 (2) 1078-1093.\\
doi:10.1093/gji/ggu314.\\

@@

(8) Martin van Driel, Lion Krischer, Simon Stahler, Kasra Hosseini, and Tarje Nissen-Meyer (2015),
\textit{Instaseis: Instant Global Broadband Seismograms Based on a Waveform Database},
To be submitted to Solid Earth\\
